Do return series have power-law tails with the same index?

### 2017-04-18 papers/FX/draft.tex
corrected the dates of the data used in the FX paper.

\documentclass[11pt,a4]{amsart}
%\usepackage{amsmath}
%\usepackage{amsthm}
%\usepackage{enumerate}
% \usepackage[bookmarks=true]{hyperref}
%% \usepackage{bookmark}
\usepackage{graphicx}
%\usepackage{multirow}
%\usepackage{adjustbox}
%\usepackage{wrapfig}
%\usepackage{subcaption}
\usepackage{color}
\usepackage[dvipsnames]{xcolor}

@@

data from 1 January 2010 to {\red why 1 January?} 1 January 2015.

@@

  \caption{\small Hill estimates $\hat \alpha_{50}$ of the lower tail indices $\alpha$ of
    daily return series in sectors of the S\&P 500
    index. The data span
    from 2010-01-01 to 2015-01-01 and comprise $n=1304$ observations.
The graphs from top to bottom correspond to the ``Energy'',
    ``Consumer Staples'' and ``Information Technology'' sectors.

@@

Yet another indication from figure \ref{fig:sectors_parameters} is
that, while the ``Energy'' and the ``Information Technology'' sectors
are similar in riskiness, the correlation between $\alpha$ and $K$ is
stronger in ``Energy''. As discussed in the last section, moving along
a curve of equal preference in the direction of increasing $\alpha$, $K$ also
increases. So the strong positive correlation seen in the ``Energy''
sector suggests these stocks might have very similar investor
preferences. This in turn may be attributed to stronger business
relations between the energy enterprises. While two IT companies
may provide a variety of products and services and not depend on each
other, two energy companies are more likely to depend on each other
via relations of supplier and customer or otherwise to compete with each
other if they are on the same link of the chain of energy production
and distribution.

@@

\bibliographystyle{unsrt}
%% \bibliography{../../thesis/econophysics}
\end{document}

>>>>

\documentclass[11pt,a4]{amsart}
%\usepackage{amsmath}
%\usepackage{amsthm}
%\usepackage{enumerate}
\usepackage[bookmarks=true]{hyperref}
%% \usepackage{bookmark}
\usepackage{graphicx}
%\usepackage{multirow}
%\usepackage{adjustbox}
%\usepackage{wrapfig}
%\usepackage{subcaption}
\usepackage{color}
\usepackage[dvipsnames]{xcolor}

@@

data from 4th Jan. 2010 to 31st Dec. 2014.

@@

  \caption{\small Hill estimates $\hat \alpha_{50}$ of the lower tail
    indices $\alpha$ of daily return series in sectors of the S\&P 500
    index. The data span from 4th Jan. 2010 to 31st Dec. 2014 and
    comprise $n=1304$ observations. The graphs from top to bottom
    correspond to the ``Energy'', ``Consumer Staples'' and
    ``Information Technology'' sectors.

@@

Yet another indication from figure \ref{fig:sectors_parameters} is
that, while the ``Energy'' and the ``Information Technology'' sectors
are similar in riskiness, the correlation between $\alpha$ and $K$ is
stronger in ``Energy''. As discussed in section \ref{sec:pareto_tail},
moving along
a curve of equal preference in the direction of increasing $\alpha$, $K$ also
increases. So the strong positive correlation seen in the ``Energy''
sector suggests these stocks might have very similar investor
preferences. This in turn may be attributed to stronger business
relations between the energy enterprises. While two IT companies
may provide a variety of products and services and not depend on each
other, two energy companies are more likely to depend on each other
via relations of supplier and customer or otherwise to compete with each
other if they are on the same link of the chain of energy production
and distribution.

@@

\bibliographystyle{unsrt}
\bibliography{../../thesis/econophysics}
\end{document}
